checkData

### 2023-08-21 analysis/checkData.Rmd
Update checkData.Rmd

@@

# list of journals in prominent sample
journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`)
```

# Journals data

@@

```{r}
d2 <- d %>%
  mutate(
    sample_journal_prominent = `Journal Name` %in% journal_list_prominent$Journal,
    sample_journal_random = `Journal Name` %in% journal_list_random$Journal,
    sample_journal_both = sample_journal_prominent & sample_journal_random,
    sample_journal_error = !sample_journal_prominent & !sample_journal_random
  )
```

```{r}
d %>% 
  count(`Journal Name`) %>%
  filter(n > 2)
```

```{r}
d %>% filter(`Journal Name` == "CLINICAL PSYCHOLOGY-SCIENCE AND PRACTICE")
```

# Articles data

@@

>>>>

# Load packages

@@

# list of journals in prominent sample
journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`)
```
# Rename colums

Rename some columns for easier reference.

```{r}
d_journals <- d_journals %>%
  select(coder_id = `Coder's Initials`,
         pilot = `Are you piloting?`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         web_comments = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
         ppc_name_B = `B. Enter the name of the PPC type offered by the journal:`,
         ppc_name_C = `C. Enter the name of the PPC type offered by the journal:`,
         ppc_description_A = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_B = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_C = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_length_A = `A. Are there any length limits for this type of PPC?`,
         ppc_length_B = `B. Are there any length limits for this type of PPC?`,
         ppc_length_C = `C. Are there any length limits for this type of PPC?`,
         ppc_time_A = `A. Are there any time limits for submission of this type of PPC?`,
         ppc_time_B = `B. Are there any time limits for submission of this type of PPC?`,
         ppc_time_C = `C. Are there any time limits for submission of this type of PPC?`,
         ppc_ref_A = `A. Are there any reference limits for this type of PPC?`,
         ppc_ref_B = `B. Are there any reference limits for this type of PPC?`,
         ppc_ref_C = `C. Are there any reference limits for this type of PPC?`,
         ppc_review_A = `A. Is this type of PPC sent for independent external peer review?`,
         ppc_review_B = `B. Is this type of PPC sent for independent external peer review?`,
         ppc_review_C = `C. Is this type of PPC sent for independent external peer review?`,
         ppc_note_A = `A. Anything additional, unusual, or interesting to note?`,
         ppc_note_B = `B. Anything additional, unusual, or interesting to note?`,
         ppc_note_C = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "), 
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

d_articles_random <- d_articles_random %>%
  select(
    article_id = `article id`,
    coder_id_primary = `primary coder initials`,
    coder_id_secondary = `secondary coder initials`,
    exclusion_primary = `1_exclusion`,
    exclsion_reason_primary = `1_exclusionReason`,
    ppc_linked_primary = `1_Is article linked to PPC`,
    notes_primary = `1_Additional notes`,
    exclusion_secondary = `2_exclusion`,
    exclsion_reason_secondary = `2_exclusionReason`,
    ppc_linked_secondary = `2_Is article linked to PPC`,
    notes_secondary = `2_Additional notes`
  )

d_articles_prominent <- d_articles_prominent %>%
  select(
    article_id = `article id`,
    coder_initials_primary = `primary coder initials`,
    coder_initials_secondary = `secondary coder initials`,
    exclusion_primary = `1_exclusion`,
    exclsion_reason_primary = `1_exclusionReason`,
    ppc_linked_primary = `1_Is article linked to PPC`,
    notes_primary = `1_Additional notes`,
    exclusion_secondary = `2_exclusion`,
    exclsion_reason_secondary = `2_exclusionReason`,
    ppc_linked_secondary = `2_Is article linked to PPC`,
    notes_secondary = `2_Additional notes`
  )
```

# Inspect journals data

@@

```{r}
d2 <- d_journals %>%
  mutate(
    sample_journal_prominent = `Journal Name` %in% journal_list_prominent$Journal,
    sample_journal_random = `Journal Name` %in% journal_list_random$Journal,
    sample_journal_both = sample_journal_prominent & sample_journal_random,
    sample_journal_error = !sample_journal_prominent & !sample_journal_random
  )
```

```{r}
d_journals %>% 
  count(`Journal Name`) %>%
  filter(n > 2)
```

```{r}
d_journals %>% filter(`Journal Name` == "CLINICAL PSYCHOLOGY-SCIENCE AND PRACTICE")
```

# Inspect articles data

@@

Our procedure is for TEH for resolve disagreements between the primary and secondary coders.

```{r}

```
